### 2018-03-11 README.Rmd
update readme and DESC

# datacitation

The goal of datacitation is to ...

@@

> Authors, (`r format(Sys.Date(), "%Y")`). _Title of compendium_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

$\textbf{Data:}$ [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

@@

>>>>

# datacitation  [![Build Status](https://travis-ci.org/benmarwick/datacitation.svg?branch=master)](https://travis-ci.org/benmarwick/datacitation)

This repository contains the data and code for our paper:

> Marwick, B., and S. Pilaar Birch (2018). "A standard for the scholarly citation of archaeological data as an incentive to data sharing" _Advances in Archaeological Practice_

Our pre-print is online here:

> Marwick, B., & S. Pilaar Birch (2018). A Standard for the Scholarly Citation of Archaeological Data as an Incentive to Data Sharing. Retrieved from osf.io/preprints/socarxiv/py4hz

@@

> Marwick, B., & S. Pilaar Birch, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for the article "A standard for the scholarly citation of archaeological data as an incentive to data sharing"_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.17605/OSF.IO/KSRUZ>

@@

**Data**: [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

@@

<sup><sub>This compendium was created with [rrtools](https://github.com/benmarwick/rrtools).</sup></sub>
